---
title: "A/B Test Analysis Report: SaaS Onboarding Experiment"
author: "Data Science Team"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: cosmo
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  fig.path = "../figures/",
  dpi = 300
)

# Set seed for reproducibility
set.seed(42)

# Load required packages
library(tidyverse)
library(infer)
library(broom)
library(patchwork)
library(gt)
library(lmtest)
library(sandwich)
library(pwr)
library(ggeffects)
```

# Executive Summary

**Purpose:** [Brief summary of the experiment's goal]

**Results:** [High-level findings - treatment effect, statistical significance, business impact]

**Recommendation:** [Ship/No-ship decision with rationale]

---

# Business Context

## Experiment Overview

- **Hypothesis:** [What we're testing and why]
- **Treatment Description:** [What changed for treatment group]
- **Success Criteria:** [Primary metric and decision threshold]
- **Duration:** [Experiment timeline]
- **Sample Size:** [N per group]

## Experiment Design

[Details on randomization unit, stratification (if any), and allocation ratio]

---

# Data Generation & Dictionary

```{r load-data}
# Load the simulated experimental data
# data <- read_csv("../data/raw/ab_test_data.csv")
```

## Data Dictionary

| Variable | Type | Description |
|----------|------|-------------|
| user_id | character | Unique user identifier |
| variant | factor | Treatment assignment (control/treatment) |
| converted | binary | Whether user completed onboarding (primary metric) |
| revenue | numeric | Revenue generated (secondary metric) |
| ... | ... | ... |

---

# Data QA & Randomization Checks

## Sample Ratio Mismatch (SRM)

```{r srm-check}
# Check for sample ratio mismatch
# Expected vs observed allocation ratios
```

**SRM Test Result:** [Pass/Fail]

## Covariate Balance

```{r balance-check}
# Test balance of pre-treatment covariates across groups
```

**Balance Assessment:** [Summary of findings]

---

# Primary Metric: Conversion

## Descriptive Statistics

```{r primary-descriptives}
# Summary statistics by variant
```

## Hypothesis Test

```{r primary-test}
# Two-proportion z-test or equivalent
# H0: p_treatment = p_control
# Ha: p_treatment != p_control
```

**Test Results:**

- Treatment conversion rate: [X%]
- Control conversion rate: [Y%]
- Absolute lift: [Z percentage points]
- Relative lift: [W%]
- p-value: [p]
- 95% CI: [[lower, upper]]

## Visualization

```{r primary-viz}
# Plot conversion rates with confidence intervals
```

---

# Secondary Metric: Revenue

```{r secondary-revenue}
# Analysis of revenue metric
# Mean comparison, t-test or Mann-Whitney
```

---

# Guardrails

```{r guardrails}
# Check guardrail metrics to ensure no negative side effects
# Examples: engagement time, feature usage, support tickets
```

---

# Segmentation & Heterogeneous Effects

```{r subgroup-analysis}
# Analyze treatment effects within key segments
# Examples: by device type, user tenure, acquisition channel
```

**Heterogeneity Findings:** [Summary of whether effects vary by subgroup]

---

# Regression-Adjusted Estimates

## CUPED / ANCOVA

```{r regression-adjusted}
# Use pre-treatment covariates to reduce variance
# ANCOVA or CUPED methodology
```

**Variance Reduction:** [X% reduction in standard error]

**Adjusted Treatment Effect:** [Effect estimate with tighter CI]

---

# Power & MDE

## Post-hoc Power Analysis

```{r power-analysis}
# Calculate achieved power given observed effect and sample size
```

**Achieved Power:** [X%]

## Minimum Detectable Effect

```{r mde-calculation}
# Calculate the minimum effect we could have detected
# with 80% power at alpha = 0.05
```

**MDE:** [X percentage points]

---

# Sensitivity Checks

## Non-parametric Tests

```{r sensitivity-nonparametric}
# Bootstrap confidence intervals
# Permutation tests
```

## Robustness to Outliers

```{r sensitivity-outliers}
# Analyze with outlier removal or winsorization
```

---

# Final Decision Memo

## Summary of Evidence

1. **Statistical Significance:** [Yes/No, p-value]
2. **Effect Size:** [Absolute and relative lift]
3. **Practical Significance:** [Business impact assessment]
4. **Guardrails:** [All passed/Any concerns]
5. **Robustness:** [Consistent across sensitivity checks]

## Recommendation

**Decision:** [Ship / Don't Ship / Iterate]

**Rationale:** [Brief explanation of decision based on evidence]

**Next Steps:** [Implementation plan or further testing needed]

---

# Appendix

## Session Info

```{r session-info}
sessionInfo()
```

## Additional Diagnostics

[Any additional plots, tables, or diagnostics]

---

**Report generated on:** `r Sys.time()`
